A Mechanical Formalization of Higher-Ranked Polymorphic Type Inference

### 2019-06-20 sections/Overview.tex
remove comments about CPS
typos

% \jimmy{Mention the implicit freshness conditions in the premises}
Please note that when we introduce a new binder in the premise, we implicitly pick a fresh one.
This applies to rules such as $\mathtt{wf_d\forall}$, $\mathtt{wf_dabs}$, $\mathtt{{\le}\forall R}$,
throughout the whole text.

@@

\jimmy{Comment A is not satisfied with the term "continuation passing style" for our definition.}

@@

\paragraph{Inference Judgments}
To express the DK's inference judgments, we use a novel form of work entries in
the worklist: our algorithmic judgment chains $\omega$. In its simplest form,
such a judgment chain is just a check, like a subtyping check $A \leq B$ or a
term typecheck $e \Leftarrow A$. 
However, the non-trivial forms of chains capture an
inference task together with the work that depends on its outcome. For
instance, a type inference task takes the form $e \Rightarrow_a \omega$.
This form expresses that we need to infer the type, say $A$, for expression $e$ and use it
in the chain $\omega$ by substituting it for the placeholder type variable $a$.
Notice that such $a$ binds a fresh type variable for the inner chain $\jg$,
which behaves similarly to the variable declarations in the context.
\bruno{Removed CPS mention here. But if we remove it here should we remove it
everywhere? Tom, your input would be good regarding this.}

>>>>

% \jimmy{Mention the implicit freshness conditions in the premises}
Note that when we introduce a new binder in the premise, we implicitly pick a fresh one.
This applies to rules such as $\mathtt{wf_d\forall}$, $\mathtt{wf_dabs}$, $\mathtt{{\le}\forall R}$,
throughout the whole text.

@@

%\jimmy{Comment A is not satisfied with the term "continuation passing style" for our definition.}

@@

\paragraph{Inference Judgments}
To express the DK's inference judgments, we use a novel form of work entries in
the worklist: our algorithmic judgment chains $\omega$. In its simplest form,
such a judgment chain is just a check, like a subtyping check $A \leq B$ or a
term typecheck $e \Leftarrow A$. 
However, the non-trivial forms of chains capture an
inference task together with the work that depends on its outcome. For
instance, a type inference task takes the form $e \Rightarrow_a \omega$.
This form expresses that we need to infer the type, say $A$, for expression $e$ and use it
in the chain $\omega$ by substituting it for the placeholder type variable $a$.
Notice that such $a$ binds a fresh type variable for the inner chain $\jg$,
which behaves similarly to the variable declarations in the context.
%\bruno{Removed CPS mention here. But if we remove it here should we remove it
%everywhere? Tom, your input would be good regarding this.}
